Scalar on Function Regression

### 2022-01-02 Presentation/slides.tex
Correction

		The principal components are then defined analogously to before:
		$$Z_j(\omega) = \int_{0}^{1} (F(\omega)(s) - \hat{\mu}(s)) \hat{\nu}_j(s) \mathrm{d}s$$

>>>>

		The $\{\hat{\nu}_i(s) \: \vert \: i \in \mathcal{I}\}$ are then called the functional principal components and the corresponding scores $\xi_i$ can be derived using the following equation.
		$$\xi_j(\omega) = \int_{0}^{1} (F(\omega)(s) - \hat{\mu}(s)) \hat{\nu}_j(s) \mathrm{d}s$$
